Geometric models reveal behavioral and neural signatures of transforming experiences into memories

### 2020-10-15 paper/main.tex
reworded caption

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/list_learning}
  \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the episode. \textbf{B}.  The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the episode.  \textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the episode.  All panels: error ribbons denote bootstrap-estimated standard error of the mean.}
  \label{fig:list-learning}
\end{figure}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Supp.\ Fig.~\corrmats).  The yellow boxes highlight the maximum correlation in each column.  The example participant's overall precision score was computed as the average across the (Fisher $z$-transformed) correlation values in the yellow boxes.  Their distinctiveness score was computed as the average (over recall events) of the $z$-scored (within column) event precisions. \textbf{B.} The across-participants (Pearson's) correlation between precision and hand-counted number of recalled scenes.  \textbf{C.} The correlation between distinctiveness and hand-counted number of recalled scenes. \textbf{D.} The correlation between precision and the number of recalled episode events, as determined by our model. \textbf{E.} The correlation between distinctiveness and the number of recalled episode events, as determined by our model.}
  \label{fig:precision-distinctiveness}
\end{figure}

>>>>

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/list_learning}
  \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the episode. \textbf{B}.  The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the episode.  \textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the episode.  All panels: error ribbons denote the bootstrap-estimated 95\% confidence interval.}
  \label{fig:list-learning}
\end{figure}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for an example participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Supp.\ Fig.~\corrmats).  The yellow boxes highlight the maximum correlation in each column.  The example participant's overall precision score was computed as the average across the (Fisher $z$-transformed) correlation values in the yellow boxes.  Their distinctiveness score was computed as the average (over recall events) of the $z$-scored (within column) event precisions. \textbf{B.} The across-participants (Pearson's) correlation between precision and hand-counted number of recalled scenes.  \textbf{C.} The correlation between distinctiveness and hand-counted number of recalled scenes. \textbf{D.} The correlation between precision and the number of recalled episode events, as determined by our model. \textbf{E.} The correlation between distinctiveness and the number of recalled episode events, as determined by our model.}
  \label{fig:precision-distinctiveness}
\end{figure}
